Concurrent Programming with CXL

### 2020-06-22 book/paper.tex
Latest
Working on starvation chapter

\section*{Exercises}
\begin{enumerate}
\item Assume that you have only binary semaphores.  Implement counting
semaphores using binary semaphores using split binary semaphores.
\item Implement a solution to the producer/consumer problem
(Figure~\ref{fig:boundedbuffer}) using split binary semaphores.
\item Suppose a sports club has only one dressing room.  The policy is that
either only women or only men may be in the dressing room together.
Implement a ``dressing room lock'' that allows multiple people to enter the
dressing room while observing the policy.
\end{enumerate}

@@

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{code/RWfair.cxl}
\end{code}
\caption{[RWfair.cxl] Reader/Writer Lock implementation addressing fairness.}
\label{fig:RWfair}
\end{figure}

@@

In this chapter, we will present a version of a reader/writer lock
implementation that solves this type of starvation.
In particular, the probability that either a reader or writer gets starved
will be exponentially diminishing.
We shall call such a solution \emph{fair}
\index{fairness}
\glsadd{fairness}
(although it does not quite
match the usual formal nor vernacular concepts of fairness).

@@

\section*{Exercises}
\begin{enumerate}
\item TBD.  starvation-free dressing room
\item TBD.  multiple GPU allocator
\end{enumerate}

>>>>

\section*{Exercises}
\begin{enumerate}
\item Assume that you have only binary semaphores.  Implement counting
semaphores using binary semaphores using split binary semaphores.
\item Implement a solution to the producer/consumer problem
(Figure~\ref{fig:boundedbuffer}) using split binary semaphores.
\item Cornell's campus features some one-lane bridges.  Cars can
only go in one direction at a time. Consider northbound
and southbound cars wanting to cross a one-lane bridge.
The bridge allows arbitrary many cars, as long as they're going in the
same direction.
Implement a lock that observes this requirement using SBS.  Write methods
\texttt{nb\_enter()} that a car must invoke before going northbound on
the bridge and \texttt{nb\_leave()} that the car must invoke after leaving
the bridge.  Similarly write \texttt{sb\_enter()} and \texttt{sb\_leave()}
for southbound cars.

\end{enumerate}

@@

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{code/RWfair.cxl}
\end{code}
\caption{[RWfair.cxl] Reader/Writer Lock SBS implementation addressing fairness.}
\label{fig:RWfair}
\end{figure}

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{code/RWqueue.cxl}
\end{code}
\caption{[RWqueue.cxl] Reader/Writer Lock SBS implementation using a queue.}
\label{fig:RWqueue}
\end{figure}

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{code/RWqtest.cxl}
\end{code}
\caption{[RWqtest.cxl] Test program for Figure~\ref{fig:RWqueue}.}
\label{fig:RWqtest}
\end{figure}

@@

In this chapter, we will present a version of a reader/writer lock
implementation that solves this type of starvation.
In particular, the probability that either a reader or writer gets starved
will be exponentially diminishing.
We shall call such a solution \emph{fair}
\index{fairness}
(although it does not quite
match the usual formal nor vernacular concepts of fairness).
\glsadd{fairness}

@@

\section*{Exercises}
\begin{enumerate}
\item Write a fair solution to the one-lane bridge problem of Chapter~\ref{ch:sbs}.
\item TBD.  multiple GPU allocator
\end{enumerate}
